
\RequirePackage{../recipe}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%% Recipe Formatting %%%%%%%

% add your formatting for the first page here
\fancypagestyle{firstpage}{%
    % here is an example
    \noredmeat
    \prepcooktime{30 minutes}{8 hours}
    \dinner
    \serves{10}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% start the recipe with the \recipe command
\recipe{Garlic Chicken Parmesan}
% set the formatting for the first page only
\thispagestyle{firstpage}
% sign every page with name and url
\sign{Patrick Cook}{https://github.com/pdcook/Recipes}

% begin writing the recipe
\ingredients
\begin{multicols}{2}
\begin{itemize}
    \item 3 lb chicken breast
    \item 3 baby red potatoes
    \item 10 cloves garlic
    \item 4 tbsp Irish butter
    \item 4 tbsp fresh thyme
    \item 4 tbsp fresh chopped parsley
    \item freshly grated Parmesan
    \item olive oil
\end{itemize}
\columnbreak
\end{multicols}

\instructions
Procure a medium-large crock-pot and a medium to large skillet.
\begin{enumerate}
    \item Cut the chicken into pieces smaller than a fist, then season the pieces with salt and pepper.
    \item Heat 1 to 2 tbsp of olive oil in the skillet on medium-high heat.
    \item Sear the chicken on all sides until golden brown. About 3 minutes per side.
    \item Wash and quarter the potatoes. Chop the garlic and parsely. Pull the leaves from the thyme. Add all to crock-pot.
    \item Add the chicken, butter, 4 heaping tbsp of grated parmesan, and 4 tbsp of oil to the crock-pot and season generously with salt and pepper. Mix everything together.
    \item Set the crock-pot pot to low and cook for 8 hours, occasionally stirring. Alternatively, set to high for 4 hours.
    \item Garnish with parmesan to taste and serve.
\end{enumerate}

\end{document}
