\RequirePackage{../recipe}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%% Recipe Formatting %%%%%%%

% add your formatting for the first page here
\fancypagestyle{firstpage}{%
    % here is an example
    \prepcooktime{20 minutes + chilling time (1+ hour)}{1 hour}
    \dessert
    \serves{6}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% start the recipe with the \recipe command
\recipe{Pumpkin Pie}
% set the formatting for the first page only
\thispagestyle{firstpage}
% sign every page with name and url
\sign{Jessica Ullom-Minnich and Patrick Cook}{https://github.com/pdcook/Recipes}

% begin writing the recipe
\ingredients

\begin{minipage}{\textwidth}
\begin{multicols*}{2}
\begin{minipage}{\linewidth}
\ingredients[Filling]
\vspace{-1.5em}
\begin{itemize}
    \item 1 $16$ oz.\ can pumpkin puree
    \item 1 $14$ oz.\ can sweetened condensed milk
    \item 2 eggs
    \item 2 tsp vanilla extract
    \item 1 tsp pumpkin pie space
    \item 1 tsp nutmeg
    \item 1 tsp cinnamon
\end{itemize}
\end{minipage}
\columnbreak

\begin{minipage}{\linewidth}
\ingredients[Crust]
\vspace{-1.5em}
\begin{itemize}
    \item $1\frac{1}{2}$ cups graham crackers, finely ground
    \item $1/3$ cup granulated sugar
    \item $6$ tbsp salted butter, melted
    \item $1/2$ tsp pumpkin pie spice
    \item $1/2$ tsp nutmeg
    \item $1/2$ tsp cinnamon
\end{itemize}

\vspace{1em}
\ingredients[Garnish]
\vspace{-1.5em}
\begin{itemize}
    \item cool whip
    \item pumpkin pie spice
\end{itemize}
\end{minipage}
\end{multicols*}
\end{minipage}
\vspace{1em}

\instructions
Procure a $9$ in.\ pie pan and plastic wrap.
\begin{enumerate}
    \item Crush the graham crackers into fine crumbs and separately melt the butter.
    \item In a medium mixing bowl, combine all the ingredients for the crust. Mix together until homogeneous.
    \item Press the mixture into the pie pan by dropping a couple spoonfuls in at a time and pressing down firmly. Ensure the crust mixture covers the entire surface of the pie pan, including the walls.
    \item Cover with plastic wrap and let chill in refrigerator for at least an hour and up to overnight.
    \item Once the pie crust has finished chilling, preheat the oven to \temp{425} and \textbf{leave the pie crust in the fridge.}
    \item In a medium mixing bowl mix together all the ingredients for the filling until homogeneous.
    \item Remove pie crust from fridge and pour pie filling into the crust. Shake gently to level filling.
    \item Bake at \temp{425} for $15$ minutes.
    \item Change the oven temperature to \temp{350}---do not remove the pie from the oven. Bake at this new temperature for $35$ to $40$ minutes, until the filling is set.\renewcommand{\thefootnote}{\fnsymbol{footnote}}\footnote[2]{The filling with firm up as the pie cools, so it may still be soft---but \textbf{not} liquid.}\renewcommand{\thefootnote}{\arabic{footnote}}
    \item Immediately after removing from the oven, garnish with additional pumpkin pie spice as desired.
    \item Allow to cool completely. Set in fridge until chilled completely. Serve cold with cool whip.
\end{enumerate}

\spewfootnotes

\end{document}
